Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-26 paper/ijcai16.tex
paper: nota per paolo

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user.  We consider three possible outcomes for a pairwise comparison between
two configurations $\vx$ and $\vx'$: either $\vx$ is preferred to $\vx'$ (written
$\vx \succ \vx'$), $\vx'$ is preferred to $\vx$ ($\vx \prec \vx'$), or there is
no clear preference between the two items ($\vx \approx \vx'$). We write
$\calD$ to denote the full set of answers elicited from the user. Queries are
typically selected so as to maximize some measure of informativeness of the
resulting responses.  Details on our actual query selection strategy will be
provided in Section~\ref{sec:formulation}.

>>>>

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user.\andrea{@PAOLO: qualche parola e reference per giustificare la scelta di pairwise queries?}  We consider three possible outcomes for a pairwise comparison between
two configurations $\vx$ and $\vx'$: either $\vx$ is preferred to $\vx'$ (written
$\vx \succ \vx'$), $\vx'$ is preferred to $\vx$ ($\vx \prec \vx'$), or there is
no clear preference between the two items ($\vx \approx \vx'$). We write
$\calD$ to denote the full set of answers elicited from the user. Queries are
typically selected so as to maximize some measure of informativeness of the
resulting responses.  Details on our actual query selection strategy will be
provided in Section~\ref{sec:formulation}.
